\documentclass{article}
\title{HW 2}
\date{2018/09/07}
\author{Yiyun Liu}
\usepackage{proof}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage[a4paper,total={6in,8in}]{geometry}
% For \mathbb{R} or \mathbb{Q}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{nameref}
\usepackage{systeme}
\usepackage{enumitem}
\begin{document}
\maketitle
\lstset{basicstyle=\ttfamily}

\section*{Page 48 - 51}
\begin{itemize}
\item [8.]
  \begin{enumerate}[label=(\alph*)]
  \item \(P(A \cup B) = P(A)+P(B)=0.3+0.5=0.8\)
  \item \(P(A - B) = P(A) = 0.3\)
  \item \(P(AB)=P(\emptyset)=0\)
  \end{enumerate}
\item [11.]
  Let $A$ be the event of an American smoking cigarettes, $B$ smoking
  cigars.
  \begin{enumerate}[label=(\alph*)]
  \item $P(A^CB^C)=P((A\cup B)^C)=1-P(A\cup B)=1-(P(A)+P(B)-P(AB))=1-(0.28+0.07-0.05)=0.7$
  \item $P(A^CB)=P(A\cup B) - P(A) = 0.3 - 0.28 = 0.02$
  \end{enumerate}
\item [16.]
  \begin{enumerate}[label=(\alph*)]
  \item $(6P5)/6^5$
  \item ${5 \choose 2}{6 \choose 1}(5P3)/6^5$
  \item ${5 \choose 2}{3 \choose 2}{6 \choose 2}{4 \choose 1} / 6^5$
  \item ${5 \choose 3}{6 \choose 1}(5P2)/6^5$
  \item $(6P2){5 \choose 3}/6^5$
  \item $(6P2){5 \choose 4}/6^5$
  \item ${6 \choose 1}/6^5$
  \end{enumerate}
\item [18.]
  ${4 \choose 1}{16 \choose 1}/ {52 \choose 2}=32/663\approx 0.0483$
\item [23.]
  $\sum_{i=1}^{6}(6-i) = 6\cdot6 - (1+6)\cdot6/2 = 15$
  $15/6^2 \approx 0.417$
\item [24.]
  I leave the fraction unsimplified so it is easier to verify that
  they sum up to $1$.\\
  \begin{tabular}{c | c}
    $i$ & P \\
    \hline
    2 & 1/36 \\
    3 & 2/36 \\
    4 & 3/36 \\
    5 & 4/36 \\
    6 & 5/36 \\
    7 & 6/36 \\
    8 & 5/36 \\
    9 & 4/36 \\
    10 & 3/36 \\
    11 & 2/36 \\
    12 & 1/36
  \end{tabular}
\item [25.]
  $P(E_n)= (1-4/36-6/36)^{n-1}(4/36) = (13/18)^{n-1}/9$.
  Since $E_n$ is a sequence of disjoint sets,
  $P(\bigcup_{n=1}^{\infty}E_n)=\sum_{n=1}^{\infty}P(E_n)$ by axiom 3.
\item [31.]
  \begin{enumerate}[label=(\alph*)]
  \item $(3P3)/3^3=6/27=2/9$
  \item $3/3^3=3/27=1/9$
  \end{enumerate}
\item [36.]
  \begin{enumerate}[label=(\alph*)]
  \item ${13 \choose 2}/{52 \choose 2} = 1/17$
  \item $13 \cdot {4 \choose 2} / {52 \choose 2} = 1/17$
  \end{enumerate}
\item [38.]
  ${3 \choose 2}/{n \choose 2} = 1/2$. Solving the equation, we get
  $n=4$. Since it's not linear, I have no idea if it's unique.
\item [41.]
  $1-5^4/6^4\approx 0.518$
\item [44.]
  \begin{enumerate}[label=(\alph*)]
  \item $3\cdot(3P3)\cdot(2P2)/(5P5) = 36/120 = 3/10$
  \item $2\cdot(3P3)\cdot(2P2)/(5P5) = 24/120 = 1/5$
  \item $(3P3)\cdot(2P2)/(5P5) = 12/120=1/10$
  \end{enumerate}
\item [49.]
  ${6 \choose 3}{6 \choose 3}/2/{12 \choose 6} = 50/231 \approx 0.216$
\item [53.]
  Problem 53 and 56 are both quite similar to matching problem, which
  makes use of the inclusion-exclusion theorem.

  Label the couples as $1$ to $4$. Define $E_i$ as the event that the
  couple $i$ sits together. What we want to compute is $P(E_1 \cup E_2
  \cup E_3 \cup E_4)$. The trick is that the subterms of the
  expression we obtained after applying the theorem are equal as long
  as they represent the union of the same number of events.

  \begin{equation*}
    \begin{split}
      1 - \frac{{4 \choose 1}\cdot 2 \cdot (7P7) - {4 \choose 2}\cdot
        2^2 \cdot (6P6) + {4 \choose 3}2^3 \cdot (5P5) - {4 \choose 4}
        \cdot 2^4 \cdot (4P4)}{8P8} 
      &= \frac{12}{35}
    \end{split}
  \end{equation*}
  When computing each subterm, we collapse the couple sitting next to
  each other as a single entity, and arrange that entity with other
  people. For instance, when we consider the event of one particular
  couple sitting next to each other, we collapse them into one object
  and compute $7P7$. Since this ``entity'' has to be arranged internally, we need
  to multiply by $2$ for each one of such couple. That's where the $2^i$s come from, when
  $i$ couples sitting next to each other. 

\item [55.]
  Yet another matching problem variation. Since it's really standard,
  I'll omit the explanations.
  \begin{enumerate}[label=(\alph*)]
  \item \[(\sum_{i=1}^{4}(-1)^{i+1}{4 \choose i} {52-2i \choose 13-2i})/{52
        \choose 13} \approx 0.2198 \]
  \item \[(\sum_{i=1}^{3}(-1)^{i+1}{13 \choose i} {52-4i \choose 13-4i})/{52
        \choose 13} \approx  0.0342 \]
  \end{enumerate}

\end{itemize}

\section*{Page 52 - 53}
\begin{itemize}
\item [5.]
  \begin{equation*}
    F_i=\begin{cases}
      E_1 & \text{if $i=1$}\\
      E_i - \bigcup_{1}^{i-1}F_j & \text{otherwise}
    \end{cases}
  \end{equation*}
  By intuition there definitely is a least fix point $F$ that
satisfies the above equation, and thus $F$ is well-defined.
  
  We claim that sequence $F_i$ satisfies the required properties.
  \begin{proof}
    When $n=1$, by recursive definition, the properties trivially
    holds.

    When $n\geq 1$, we show that the property holds for $n+1$,
    by assuming it holds for $n$.
    
    \begin{equation*}
      \begin{split}
        \bigcup_{1}^{n+1}F_j
        &= \bigcup_{1}^{n}F_j \cup F_{n+1} \\
        &= \bigcup_{1}^{n}F_j \cup (E_{n+1} - \bigcup_{0}^{n}F_j)\\
        &= \bigcup_{1}^{n}F_j \cup E_{n+1}\\
        &= \bigcup_{1}^{n}E_j \cup E_{n+1}\\
        &= \bigcup_{1}^{n+1}E_j
      \end{split}
    \end{equation*}

    Since $F_1$ to $F_n$ are already disjoint, we only need to show
    that $F_{n+1}$ is disjoint with any $F_i$ such that $i\neq n+1$.

    Suppose $x \in F_i$ for $i \neq
    n+1$, and suppose $x \in F_{n+1}$. By definition of $F_{n+1}$, $x
    \in E_n-\bigcup_{1}^{n}F_j$. Therefore, $x \notin
    \bigcup_{1}^{n}F_j$, which simply says that $x$ doesn't belong to
    any $F_j$ when $i$ is between $1$ and $n$. $x \notin F_i$. Contradiction.
  \end{proof}
\item [10.]
  I remember the following fact was proved in class, but just in case:
  \begin{equation*}
    \begin{split}
      P(E \cup F \cup G)
      &= P ((E \cup F) \cup G) \\
      &= P(E \cup F) + P(G) - P((E\cup F) G)\\
      &= P(E) + P(F) - P(EF) + P(G) - P(EG \cup FG) \\
      &= P(E) + P(F) + P(G) - P(EF) - (P(EG) + P(FG) - P(EFG))\\
      &= P(E) + P(F) + P(G) - P(EF) - P(EG) - P(FG) + P(EFG)\\
    \end{split}
  \end{equation*}

  Therefore, to prove the statement, we only need to show the
  equality:
  \begin{equation*}
     - P(EF) - P(EG) - P(FG) + P(EFG) =  - P(E^CFG) - P(EF^CG) -
     P(EFG^C) - 2P(EFG)
  \end{equation*}
  holds.

  \begin{equation*}
    \begin{split}
      &- P(EF) - P(EG) - P(FG) + P(EFG) + P(E^CFG) + P(EF^CG) +
      P(EFG^C) + 2P(EFG) \\
      &= (P(EFG) + P(E^CFG) - P(FG)) + (P(EFG) + P(EF^CG) - P(EG)) +
      (P(EFG) + P(EFG^C)-P(EF))\\
      &= (P(FG)-P(FG)) + (P(EG)-P(EG)) + (P(EF)-P(EF))\\
      &= 0
    \end{split}
  \end{equation*}
  Moving  terms on the right of $P(EFG)$ to right-hand-side of $=$
  completes the proof.
\item [11.]
  \begin{proof}
    I'll just jump to the general case.

    $P(E) + P(F) -P(EF) = P(E\cup F) \leq 1$. The less than $1$ part
    is directly from axiom.

    Moving $P(EF)$ to right and $1$ to left, we get
    $P(EF) \geq P(E)+P(F)-1$
  \end{proof}
\item [12.]
  \begin{equation*}
    \begin{split}
      P((E\cup F) - EF)  + P(EF)
      &= P(((E \cup F) - EF) \cup EF)\\
      &= P(E \cup F)\\
      &= P(E) + P(F) - P(EF)
    \end{split}
\end{equation*}
Moving the first $P(EF)$ to the right-hand side of $=$:
$P((E\cup F) - EF) = P(E) + P(F) - 2P(EF)$

\end{itemize}



\end{document}
