\documentclass{article}
\title{HW 3}
\date{2018/09/13}
\author{Yiyun Liu}
\usepackage{proof}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage[a4paper,total={6in,8in}]{geometry}
% For \mathbb{R} or \mathbb{Q}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{nameref}
\usepackage{systeme}
\usepackage{comment}
\usepackage{enumitem}
\begin{document}
\maketitle
\lstset{basicstyle=\ttfamily}

\section*{Extra}
We need to find all solutions for this equation:
$ord(n)=\frac{48}{\gcd(48,n)}=8$, which is the same as $\gcd(48,n) =
6$.

The following perl6 one-liner finds the solutions easily:
\begin{lstlisting}
grep 1..48: * gcd 48 == 6
\end{lstlisting}

It gives $6,18,30,42$, which is exactly what we want.

\section*{Exercises 6}
\begin{itemize}
\item [32.]
  \begin{itemize}
  \item [e.] true.
    \begin{proof}
      Suppose $a$ and $b$ are elements of some cyclic group $G$. We have $a=g^m$ and $b=g^n$ for some element $g$. $ab = g^{m+n} = g^{n+m}=ba$.
    \end{proof}
    Every cyclic group is abelian, and for any finite order $n$, there
    is a cyclic/abelian group $\mathbb{Z}_n$
  \item [f.] false\\
    \begin{tabular}{c | c c c c }
      $\cdot$&e&a&b&c\\
      \hline
      e&e&a&b&c\\
      a&a&e&c&b\\
      b&b&c&e&a\\
      c&c&b&a&e
    \end{tabular}
    The above group has order $4$ but not cyclic. 
  \item [g.] false.
    $1$ is a generator of $\mathbb{Z}_{20}$ but it's not a prime number.
  \item [h.] false. The set $\{0\}$ and $\mathbb{Z}^*$ are both groups under multiplication, but their intersection is not even a non-empty set.
  \item [i.] true.
    \begin{proof}
      $e$ is clearly in $H \cap K$, since both $H$ and $K$ have neutral element inherited from $G$.

      Suppose $a \in H \cap K$ and $b \in H \cap K$. $a,b\in H$ and $a,b \in K$. Since the operation is closed under both $H$ and $K$, $ab \in H$ and $ab \in K$, and hence $ab \in H \cap K$.

      Suppose $a \in H \cap K$. $a \in H$ and $a \in K$, and thus
      there is an inverse of $a$ in $H$ and an inverse of $a$ in $K$. $H$ and $K$ are subgroups of $G$, so the two inverses are inverses of $a$ in $G$. Because we know inverse of $a$ is unique in $G$, the two inverses are equal. Let's call this element $b$. $b \in H \cap K$ and $b$ satisfies the properties for inverse of $a$. $a$ has an inverse in $H \cap K$.
    \end{proof}
  \item [j.] true.
    \begin{proof}
      Let $g$ be a generator for the group, where $|\langle g \rangle|=k$. Because $k>2$, $k-1$ and $1$ are both relatively prime to $k$. By theorem 6.14, $g^{k-1}$ and $g$ are two generators of this group. They are clearly distinct, as proved in textbook.
    \end{proof}
  \end{itemize}
\end{itemize}

\section*{Exercises 8}
\begin{itemize}
\item [4.]
  \[\begin{pmatrix}
    1 & 2 & 3 & 4 & 5 & 6\\
    5 & 1 & 6 & 2 & 4 & 3
  \end{pmatrix}\]
\item [16.]
  $3P3 = 3! = 6$. One element is fixed, so we count only the permutation of the rest of three elements on three remaining slots.
\item [18.]
  \begin{enumerate}[label=\alph*.]
  \item
    \[\langle \rho_1 \rangle = \{\rho_0, \rho_1, \rho_2\}\]
    \[\langle \rho_2 \rangle = \{\rho_0, \rho_1, \rho_2\}\]
    \[\langle \mu_1 \rangle = \{\rho_0, \mu_1\}\]
  \item Handwritten on the last page. It might seem like it
    lacks proof of work, but with some nice theorems it can be done
    without writing much down. First, with Langrange's Theroem, we
    know the size of subsets could only be $1,2,3,6$. Second, we know
    the subgroups form a lattice. We start with the cyclic subgroups and
    the trivial subgroup. By taking the closure of the union of two
    subgroups we already have, we form a new subgroup. The new
    subgroup is usually easy to derive. For example, if
    the new subgroup has at least $4$ elements, we can conclude it is
    the improper subgroup. If we keep building 
  \end{enumerate}
\item [20.]
  \begin{proof}
    $S_3$ has six elements but is not a cyclic group, and therefore
    $S_3 \ncong \mathbb{Z}_6$. Let's call the group generated by
    $\rho$ $P$. $P$ has six elements, and $P$ is cyclic.
    $P \cong \mathbb{Z}_6$.

    \begin{equation*}
      \begin{split}
        \rho^0 =
        \begin{pmatrix}
          1 & 2 & 3 & 4 & 5\\
          1 & 2 & 3 & 4 & 5
        \end{pmatrix}\\
        \rho^1 =
        \begin{pmatrix}
          1 & 2 & 3 & 4 & 5\\
          2 & 4 & 5 & 1 & 3
        \end{pmatrix}\\
        \rho^2 =
        \begin{pmatrix}
          1 & 2 & 3 & 4 & 5\\
          4 & 1 & 3 & 2 & 5
        \end{pmatrix}\\
        \rho^3 =
        \begin{pmatrix}
          1 & 2 & 3 & 4 & 5\\
          1 & 2 & 5 & 4 & 3
        \end{pmatrix}\\
        \rho^4 =
        \begin{pmatrix}
          1 & 2 & 3 & 4 & 5\\
          2 & 4 & 3 & 1 & 5
        \end{pmatrix}\\
        \rho^5 =
        \begin{pmatrix}
          1 & 2 & 3 & 4 & 5\\
          4 & 1 & 5 & 2 & 3
        \end{pmatrix}
      \end{split}
    \end{equation*}

    Since isomorphism is transitive,
    $S_3 \ncong \mathbb{Z}_6 \cong P$. They are not isomorphic.

    As for why $S_3$ is not cyclic, one can tell from problem $18$, or
    by the simple observation that flip and rotation are not
    commutative and hence it's not even abelian.

  


  \end{proof}
    I probably
    misinterpreted the question since the table is always trivial for a
    cyclic group:
    
% BEGIN RECEIVE ORGTBL mul
\begin{tabular}{l|llllll}
\(\circ\) & \(\rho^0\) & \(\rho^1\) & \(\rho^2\) & \(\rho^3\) & \(\rho^4\) & \(\rho^5\)\\
\hline
\(\rho^0\) & \(\rho^0\) & \(\rho^1\) & \(\rho^2\) & \(\rho^3\) & \(\rho^4\) & \(\rho^5\)\\
\(\rho^1\) & \(\rho^1\) & \(\rho^2\) & \(\rho^3\) & \(\rho^4\) & \(\rho^5\) & \(\rho^0\)\\
\(\rho^2\) & \(\rho^2\) & \(\rho^3\) & \(\rho^4\) & \(\rho^5\) & \(\rho^0\) & \(\rho^1\)\\
\(\rho^3\) & \(\rho^3\) & \(\rho^4\) & \(\rho^5\) & \(\rho^0\) & \(\rho^1\) & \(\rho^2\)\\
\(\rho^4\) & \(\rho^4\) & \(\rho^5\) & \(\rho^0\) & \(\rho^1\) & \(\rho^2\) & \(\rho^3\)\\
\(\rho^5\) & \(\rho^5\) & \(\rho^0\) & \(\rho^1\) & \(\rho^2\) & \(\rho^3\) & \(\rho^4\)\\
\end{tabular}
% END RECEIVE ORGTBL mul
\begin{comment}
#+ORGTBL: SEND  mul orgtbl-to-latex :splice nil :skip 0
| $\circ$  | $\rho^0$ | $\rho^1$ | $\rho^2$ | $\rho^3$ | $\rho^4$ | $\rho^5$ |
|----------+----------+----------+----------+----------+----------+----------|
| /        | <        |          |          |          |          |          |
| $\rho^0$ | $\rho^0$ | $\rho^1$ | $\rho^2$ | $\rho^3$ | $\rho^4$ | $\rho^5$ |
| $\rho^1$ | $\rho^1$ | $\rho^2$ | $\rho^3$ | $\rho^4$ | $\rho^5$ | $\rho^0$ |
| $\rho^2$ | $\rho^2$ | $\rho^3$ | $\rho^4$ | $\rho^5$ | $\rho^0$ | $\rho^1$ |
| $\rho^3$ | $\rho^3$ | $\rho^4$ | $\rho^5$ | $\rho^0$ | $\rho^1$ | $\rho^2$ |
| $\rho^4$ | $\rho^4$ | $\rho^5$ | $\rho^0$ | $\rho^1$ | $\rho^2$ | $\rho^3$ |
| $\rho^5$ | $\rho^5$ | $\rho^0$ | $\rho^1$ | $\rho^2$ | $\rho^3$ | $\rho^4$ |

\end{comment}
\end{itemize}


\end{document}
